---
title: "p8105_hw1_jz3902"
author: "Jinghan Zhao"
date: "2024-09-21"
output: github_document
---

This is HW1 of P8105.

```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)
```

## Problem 1

### Load the `penguins` dataset

```{r load_dataset}
data("penguins", package = "palmerpenguins")
```

### Description of the `penguins` dataset

1.  Variable names and values

Here's the first few rows of them.

```{r variables}
head(penguins)
```


2.  Size of the dataset

The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.


3.  The mean flipper length

```{r mean_flipper_length}
penguins %>% 
  pull(, flipper_length_mm) %>% 
  mean(, na.rm = FALSE)
```


4.  A scatterplot of flipper length VS bill length

Firstly, remove rows containing missing values.

Then, draw and save the plot.

Y is flipper length (mm), X is bill length (mm), colored by species.

```{r scatterplot}
penguins %>% 
  drop_na() %>% 
  ggplot() +
  geom_point(
    aes(x = bill_length_mm, 
        y = flipper_length_mm, 
        color = species)
    )

ggsave("scatterplot.png")
```


