---
title: "p8105_hw1_jz3902"
author: "Jinghan Zhao"
date: "2024-09-21"
output: github_document
---

This is HW1 of P8105.

```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)
```

## Problem 1

### Load the `penguins` dataset

```{r load_dataset}
data("penguins", package = "palmerpenguins")
```

### Description of the `penguins` dataset

**Variable names and values**

Here's the first few rows of them.

```{r variables}
head(penguins)
```


**Size of the dataset**

The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.


**The mean flipper length**

```{r mean_flipper_length}
penguins %>% 
  pull(, flipper_length_mm) %>% 
  mean(, na.rm = FALSE)
```


**A scatterplot of flipper length VS bill length**

Firstly, remove rows containing missing values.

Then, draw and save the plot.

Y is flipper length (mm), X is bill length (mm), colored by species.

```{r scatterplot}
penguins %>% 
  drop_na() %>% 
  ggplot() +
  geom_point(
    aes(x = bill_length_mm, 
        y = flipper_length_mm, 
        color = species)
    )

ggsave("scatterplot.png")
```


## Problem 2

### Create the data frame

The data frame is comprised of:

`norm_samp` : a random sample of size 10 from a standard normal distribution.

`samp_g0` : a logical vector indicating whether elements of the sample are greater than 0.

`vec_char` : a character vector of length 10.

`vec_factor` : a factor vector of length 10, with 3 different factor “levels”.

```{r create_df}
df = 
  tibble(
    norm_samp = rnorm(n = 10),
    samp_g0 = norm_samp > 0,
    vec_char = sample(letters, 10, replace = TRUE),
    vec_factor = factor(
        sample(c("A", "B", "C"), 10, replace = TRUE)
        )
    )

df

```


### Calculate the mean of each variable

Calculate the mean with `pull()`.

**Mean of numeric sample**

```{r mean_normal}
df %>% 
  pull(norm_samp) %>% 
  mean()
```

**Mean of logical vector**

```{r mean_logical}
df %>% 
  pull(samp_g0) %>% 
  mean()
```

**Mean of character vector**

```{r mean_char}
df %>% 
  pull(vec_char) %>% 
  mean()
```

**Mean of factor vector**

```{r mean_factor}
df %>% 
  pull(vec_factor) %>% 
  mean()
```

The mean can be computed on numeric sample and logical vector, but not on character and factor vector.

### Convert variables to numeric

```{r convert_var, warning = FALSE, results = 'hide'}
df %>% 
  pull(samp_g0) %>% 
  as.numeric()

df %>% 
  pull(vec_char) %>% 
  as.numeric()

df %>% 
  pull(vec_factor) %>% 
  as.numeric()
```

By converting to numeric, the mean can be calculated for logical and factor variables, but not for character variables.

**Discussion:**

The logical variables can be converted to numeric as value 0 or 1, so the mean can be calculated.

The character variables cannot be converted to numeric, and the mean cannot be calculated.

The factor variables can be converted to numeric values, but the mean cannot be calculated. Calculating the mean of factor variables may not be of practical significance, and the factor "levels" should not be analyzed by simple addition and subtraction operations.

