---
title: "p8105_hw1_jz3902"
author: "Jinghan Zhao"
date: "2024-09-21"
output: github_document
---

This is HW1 of P8105.

```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)
```

## Problem 1

### Load the `penguins` dataset

```{r load_dataset}
data("penguins", package = "palmerpenguins")
```

### Description of the `penguins` dataset

1.  Variable names and values

Here's the first few rows of them.

```{r variables}
head(penguins)
```


2.  Size of the dataset

The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.


3.  The mean flipper length

```{r mean_flipper_length}
penguins %>% 
  pull(, flipper_length_mm) %>% 
  mean(, na.rm = FALSE)
```


4.  A scatterplot of flipper length VS bill length

Firstly, remove rows containing missing values.

Then, draw and save the plot.

Y is flipper length (mm), X is bill length (mm), colored by species.

```{r scatterplot}
penguins %>% 
  drop_na() %>% 
  ggplot() +
  geom_point(
    aes(x = bill_length_mm, 
        y = flipper_length_mm, 
        color = species)
    )

ggsave("scatterplot.png")
```


## Problem 2

### Create the data frame

The data frame is comprised of:

`norm_samp` : a random sample of size 10 from a standard normal distribution.

`samp_g0` : a logical vector indicating whether elements of the sample are greater than 0.

`vec_char` : a character vector of length 10.

`vec_factor` : a factor vector of length 10, with 3 different factor “levels”.

```{r create_df}
df = 
  tibble(
    norm_samp = rnorm(n = 10),
    samp_g0 = norm_samp > 0,
    vec_char = sample(letters, 10, replace = TRUE),
    vec_factor = factor(
        sample(c("A", "B", "C"), 10, replace = TRUE)
        )
    )

df

```


### Calculate the mean of each variable

Calculate the mean with `pull()`.

**Mean of numeric sample**

```{r mean_normal}
df %>% 
  pull(norm_samp) %>% 
  mean()
```

**Mean of logical vector**

```{r mean_logical}
df %>% 
  pull(samp_g0) %>% 
  mean()
```

**Mean of character vector**

```{r mean_char}
df %>% 
  pull(vec_char) %>% 
  mean()
```

**Mean of factor vector**

```{r mean_factor}
df %>% 
  pull(vec_factor) %>% 
  mean()
```

The mean can be computed on numeric sample and logical vector, but not on character and factor vector.
